{CPU-Scheduling}

### 2024-12-11 LaTeX/Sources/Advanced.tex
Finished ticket currencies

\section{Operations of Tickets}

@@

>>>>

\section{Operating with Tickets}

@@

\section{Ticket Currencies}

Ticket currencies are a way for parent processes to manage their child processes.
Yes, that's right, not all processes are built the same.
A child process is a process that is created by another process.
A parent process is a process, which has atleast one child process.
A job can be both at the same time.

The idea behind ticket currencies is that a parent process creates its own unique currency. Therefore he himself can distribute as many bills as he wants. 
However more custom bills does not equal to a higher share of CPU time in the whole system.
Take figure \ref{fig:ticket-currencies} for example. Even though process A had created 100 tickets and gave 40 to process A$_1$ in the end it is all about ratios.
Therefore the overall runtime that A$_1$ has is:

$$\frac{20\text{T}_\text{G}}{50\text{T}_\text{G}} * \frac{40\text{T}_\text{A}}{100\text{T}_\text{A}} = 0.16 \Rightarrow 16\%$$

There is another hidden benefit. If the parent process recieves more global tickets, than if it has a custom currency, there are no further things to do.
If however it does not have a custom currency than the process has to transfer these new tickets to the child processes. Overall it can get very messy all too quickly.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{Assets/Ticket-Currency.pdf}
    \caption{Example of a Custom Ticket Currency}
    \label{fig:ticket-currencies}
\end{figure}

Another benefit comes with the ticket inflation or deflation operation, which can only be used by the owner of the currency.
This is the case, because it involves creating or destroying tickets. 
Still unlike the ticket transfer, ticket inflation does not need a sender and reciever.
The selected process just get more tickets assigned.
With this the parent process changes the ration of ownership and therefore boosts the selected job.
